---
title: "rpubs.com/forestgeo/gh2"
subtitle: "GitHub Tutorial 2"
author: "maurolepore@gmail.com"
date: "25 July 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Goal | Interact with GitHub from RStudio

Requisites ([Initial Set up](https://github.com/forestgeo/learn/issues/31))

- GitHub account.
- Git installed in your computer.
- RStudio installed in your computer.

# 2. Why and how to use git | [Git for Humans](https://speakerdeck.com/alicebartlett/git-for-humans)

## Why using git

- [With dropbox](https://speakerdeck.com/alicebartlett/git-for-humans?slide=22)

- With Git

    - [Express why things change](https://speakerdeck.com/alicebartlett/git-for-humans?slide=36)

    - [Try new things savely](https://speakerdeck.com/alicebartlett/git-for-humans?slide=64)
    
    - [Collaborate](https://speakerdeck.com/alicebartlett/git-for-humans?slide=75)

## How you can use git | Here we will use RStudio.

- **From RStudio.**

- **From a GUI* (
[Recommended Git clients](http://happygitwithr.com/git-client.html#recommended-git-clients)).**

- **From a shell such as bash. **

## Hands on

How many people installed git?

(If you haven't, sit next to someone that has already installed git.)

## 

### Open a new repo on GitHub

### Then clone the repo into an RStudio project.

## Fork

### Fork forestr/tutorials into your personal account.

### Clone forestr/tutorials into an RStudio project.

### Change something locally, e.g. README. Then push.

### Confirm the change in your fork.

## Pull request

### Request to pull your your fork into forestr/tutorials

### Push from your computer to an empty new project





If you get lost, don't worry. You can catch up later by asking me or reading:

- http://r-pkgs.had.co.nz/git.html. 
- http://happygitwithr.com/

## Resources

Watch webinars listed on `articles/Learning_road_map.docx`



```{r}
tag_xxxcont <- "Incorporate content into slides; check slides."

```


- Quickly review the last tutorial. Show:
    - forestgeo GitHub organization.
    - forestr package website.
    - rpubs.com/forestgeo.
    - twitter.com: search for #forestgeo #pr17.

- Get GitHub usernames
    - check whose invitation is pendent.
    - those who haven't yet contacted me via GitHub,  ask to comment this issue.

- Download, upload single files.

- Create, delete, clone and fork repos
   - Open a new repo on GitHub, then clone it into a new RStudio project.
       - Update readme on RStudio, then push.
       - Update readme on GitHub, then pull.
   - Clone the preexisting __gh2__ repo from GitHub into an RStudio project.
       - Repeat as above.
   - Fork a repo form some other GitHub account into yours.
       - Repeat as above.
   - Add a remote to push a preexisting repo from RStudio into a new repository on GitHub.

- Time travel
    - See history
    - Revert file

If you get lost, don't worry. You can catch up later by asking me or reading:

- http://r-pkgs.had.co.nz/git.html. 
- http://happygitwithr.com/



























# GitHub tutorial 3 | Workflow with GitHub Flow

## Workflows may be simple or complex | Simple is better than complex; complex is better than complicated.

Simple workflow model adviced by github

- https://guides.github.com/introduction/flow/

- http://scottchacon.com/2011/08/31/github-flow.html

General models, including those not adviced by github

- https://www.atlassian.com/git/tutorials/comparing-workflows/forking-workflow



